An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/concl.tex
config: concl

Our \app prototype still has many limitations. 
For example, we cannot handle configuration errors that can be 
triggered during system execution time, 
and we cannot detect misconfiguration across software components. 
Nevertheless, we believe \app represent a practical path
toward automatic language-based configuration verification.

>>>>

Our \app prototype still has many limitations. 
For example, we cannot handle configuration errors that can be 
triggered during system execution time, 
and we cannot detect misconfiguration across software components
maintained by different parties. 
Nevertheless, we believe \app represent a practical path
toward automatic language-based configuration verification.
